---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(crayon.enabled = TRUE, width = 1024)
fansi::set_knit_hooks(knitr::knit_hooks)

```

# joblog

An example package to show how custom "virtual event types" can be leverage
to easily create powerfull logging infrastructure
<!-- badges: start -->
<!-- badges: end -->


## Installation

``` r
remotes::install_github("s-fleck/joblog")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, width = 1000}
library(joblog)

lf <- paste0(tempfile(), ".jsonl")
on.exit(unlink(lf))
lg <- lgr::get_logger("jobs")$set_propagate(FALSE)
lg$add_appender(lgr::AppenderJson$new(file = lf))

# normal job
lg$list_log(job_start("example", repeats = Sys.Date(), timestamp = Sys.Date() - 1L))
lg$list_log(job_finished())  # mark the last job as finished

# job that repeats tomorrow
lg$list_log(job_start("example", repeats = Sys.Date() + 1L))
lg$list_log(job_finished())

# job that repeats today
lg$list_log(job_start("example-due-today", repeats = Sys.Date(), timestamp = as.POSIXct(Sys.Date() - 1L)))
lg$list_log(job_finished())

# job that is overdue repeats today
lg$list_log(job_start("example-overdue", repeats = Sys.Date()-1L, timestamp = as.POSIXct(Sys.Date() - 2L)))
lg$list_log(job_finished())

# currently running job
lg$list_log(job_start("example-still-running"))

```

joblog provides helpers to extract jobs from a .jsonl log and comes with a print
method that colors jobs whether they are overdue, due today or still running

```{r}
print(scrape_joblog(lf))
```


```
#cleanup
unlink(lf)

```
